### 2022-08-05 main/chapter_2ljets.tex
move orthogonal region impact to design section

\begin{singlespacing}
\chapter{A search for new phenomena}
\label{chapter:2ljets}
%
\begin{epigraphs}
\qitem{%
An experiment is never a failure solely because it fails to
achieve predicted results. An experiment is a failure only when it also
fails adequately to test the hypothesis in question, when the data it
produces don’t prove anything one way or another.%
}%
{Robert~M.~Pirsig,
\emph{Zen and the Art of Motorcycle Maintenance},
1974~\cite{pirsig1999zen}}
\qitem{%
But there is one feature I notice that is generally missing in cargo cult
science. \ldots\
% That is the idea that we all hope you have learned in studying science in
% school--we never say explicitly what this is, but just hope that you catch
% on by all the examples of scientific investigation. It is interesting,
% therefore, to bring it out now and speak of it explicitly.
It's a kind of scientific integrity, a principle of scientific thought that
corresponds to a kind of utter honesty --- a kind of leaning over backwards.%
}%
{Richard~Feynman,
\emph{Cargo Cult Science},
1974~\cite{feynman1974cargo}}
\end{epigraphs}
\end{singlespacing}

@@

This chapter follows a questionable order.
It may be clearer, and is certainly more ordinary,
to first present preparations (blind to data),
followed later by the results (unblinded).
Instead, this chapter first reports the unblinded results, then follows with
in-depth discussions of individual elements, partially in light of those
results.
I choose this order for two reasons.
First, it avoids iterating over those elements twice, once before and again
after unblinding.
The analysis has many little and loosely related pieces that I attempt to
to cover locally to reduce jumps between far-flung corners of the
chapter.
Second, and sadly, many design decisions can only be explained in light of the
unblinded results, since important aspects were reworked in the
$19$~months between its unblinding and eventual publication.

There are certain plots and tables which, personally, I first seek when
meeting an \atlas\ search paper, particularly the summary plot with all signal
regions and the model-dependent exclusion contours.
This chapter begins by presenting those results in brief in Section
~\ref{sec:2ljets_splash}.
The meat of the chapter follows.
\begin{itemize}
\item Context from previous searches and inspirations for the design goals
of the $\twoljets$-electroweak search are described in
Section~\ref{sec:2ljets_context}.
\item Data, their event variables and the reconstructed objects from which
they derive are described in Section~\ref{sec:2ljets_events}.
\item Region design for the $\twoljets$-electroweak search is described and
explained in Section~\ref{sec:2ljets_design}.
\item The modelling of our uncertain predictions of background and signal
contributions in those regions is covered in
Section~\ref{sec:2ljets_modelling}.
\item Some validation studies are presented in Section~\ref{sec:2ljets_validation}.
\item The unblinding procedure of this search is discussed in
Section~\ref{sec:2ljets_unblinding}, and
\item we recap the search results in Section~\ref{sec:2ljets_results}.
\end{itemize}

@@

Uniquely to Low regions, and signal models with small mass-splitting, it is
seen (in Figure~\ref{fig:2ljets_low_minus_norll_nomt2_mt2}) that substantial
signal yields exist at small $\mttwoll$.
To capture these signals, SR-Low-2 is defined as the only
$\twoljets$-electroweak region with $\mttwoll < 80\,\eV[G]$.
That threshold of $80\,\eV[G]$ is not very important.
After the other selections for SR-Low-2, almost all signal and background
samples are in the spike near zero;
a lower requirement would make little difference, and $80\,\eV[G]$ matches
other, usually inverted, selections.

@@

@@

\TODO{consider moving this to region design?}
Preliminary projected exclusion contours that separate the use only subsets
of our signal regions to assess their effects are displayed in
Figure~\ref{fig:2ljets_fit_muti_contourss}.

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_c1n2.pdf}
\caption{C1N2}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_gmsb.pdf}
\caption{GMSB}
\end{subfigure}
\caption[
Projected exclusion from sets of orthogonal signal regions
]{%
Projected exclusion from sets of orthogonal signal regions, demonstrating that
their combination has greater sensitivity reach than any individually.
The label `High' indicates the bins of SR-High, and `HighNo4' excludes
SR-High-1J to show the locations where mono-jet events have an impact.
Similarly, `$\llbb$', `Int', `Low', and `OffShell' are shown to target their
appropriate parameter spaces.
Although figures were produced before unblinding, with older samples and region
designs, the general message has not changed.
Values of $\cls$ from expected (not observed --- the label is wrong) data in
the combined fit are overlaid on the grid.
}
\label{fig:2ljets_fit_muti_contourss}
\end{figure}

>>>>

\begin{singlespacing}
\chapter{A search for new phenomena}
\label{chapter:2ljets}
%
\begin{epigraphs}
\qitem{%
An experiment is never a failure solely because it fails to
achieve predicted results. An experiment is a failure only when it also
fails adequately to test the hypothesis in question, when the data it
produces don’t prove anything one way or another.%
}%
{Robert~M.~Pirsig,
\emph{Zen and the Art of Motorcycle Maintenance},
1974~\cite{pirsig1999zen}}
\qitem{%
But there is one feature I notice that is generally missing in cargo cult
science. \ldots\
% That is the idea that we all hope you have learned in studying science in
% school --- we never say explicitly what this is, but just hope that you catch
% on by all the examples of scientific investigation. It is interesting,
% therefore, to bring it out now and speak of it explicitly.
It's a kind of scientific integrity, a principle of scientific thought that
corresponds to a kind of utter honesty --- a kind of leaning over backwards.%
}%
{Richard~Feynman,
\emph{Cargo Cult Science},
1974~\cite{feynman1974cargo}}
\end{epigraphs}
\end{singlespacing}

@@

This chapter follows a questionable order.
It may be clearer, and is certainly more ordinary,
to first present preparations (blind to data),
followed later by the results (unblinded).
Instead, this chapter first reports the unblinded results, then follows with
in-depth discussions of individual elements, partially in light of those
results.
I choose this order for two reasons.
Firstly, it avoids iterating over those elements twice, once before and again
after unblinding.
The analysis has many little and loosely related pieces that I attempt to
to cover locally to reduce jumps between far-flung corners of the
chapter.
Secondly, and sadly, many design decisions can only be explained in light of the
unblinded results, since important aspects were reworked in the
nineteen months between its unblinding and eventual publication.

There are certain plots and tables which, personally, I first seek when
meeting an \atlas\ search paper, particularly the summary plot with all signal
regions and the model-dependent exclusion contours.
This chapter begins by presenting those results in brief in Section
~\ref{sec:2ljets_splash}.
The meat of the chapter follows.
\begin{itemize}
\item Context from previous searches and inspirations for the design goals
of the $\twoljets$-electroweak search are described in
Section~\ref{sec:2ljets_context}.
\item Data, their event variables and the reconstructed objects from which
they derive are described in Section~\ref{sec:2ljets_events}.
\item Region design for the $\twoljets$-electroweak search is described and
explained in Section~\ref{sec:2ljets_design}.
\item The modelling of our uncertain predictions of background and signal
contributions in those regions is covered in
Section~\ref{sec:2ljets_modelling}.
\item Some validation studies are presented in
Section~\ref{sec:2ljets_validation}.
\item The unblinding procedure of this search is discussed in
Section~\ref{sec:2ljets_unblinding}, and
\item and some additional results are presented in
Section~\ref{sec:2ljets_results}.
\TODO{Conclusions}
\end{itemize}

@@

Uniquely to Low regions, and signal models with small mass-splitting, it is
shown in Figure~\ref{fig:2ljets_low_minus_norll_nomt2_mt2} that substantial
signal yields exist at small $\mttwoll$.
To capture these signals, SR-Low-2 is defined as the only
$\twoljets$-electroweak region with $\mttwoll < 80\,\eV[G]$.
That threshold of $80\,\eV[G]$ is not very important.
After the other selections for SR-Low-2, almost all signal and background
samples are in the spike near zero;
a lower requirement would make little difference, and $80\,\eV[G]$ matches
other, usually inverted, selections.

@@

\subsection{Impact}
\label{sec:2ljets_imapct}
We have now seen the definitions of OffShell, Low, Intermediate and High
regions, how their designs intend to target certain regions of parameter space,
and how example signal models can create visible effects in those regions.
To further demonstrate that these regions work as intended,
Figure~\ref{fig:2ljets_fit_multi_contours} presents projected exclusion
contours generated from fits with subsets of the signal regions.
For each contour, fits are performed with only the control regions and one
subset of the signal regions as labelled and described in the figure caption.

Combining all regions provides greater exclusion than any individual contour,
and avoids the sharp corners that could have been assigned by stitching those
individual parts together.
That confirms that our design of combined, orthogonal regions works as
intended.
In most locations, however, most exclusion is attributable to only one subset
of the regions.
That shows that the combination is a relatively minor refinement that may or
may not be worth the cost of implementing it.

At the highest $m(\chargino_1,\neutralino_2)$ edge of the C1N2 contours,
the inclusion of SR-High-1J (in addition to all other SR-High bins) is shown
to extend the exclusion by around $60\,\eV[G]$.
Across the rest of the C1N2 grid, each set of regions is impacting its targeted
parameter space.
Sensitivity to the C1N2 ($200$, $100$) point was a goal of the SR-Low design,
and although it alone does not quite achieve expected exclusion there, the
combination with other regions does.

For GMSB, only SR-$\llbb$ has sensitivity to large
$B(\neutralino_1 \rightarrow h \tilde{G})$ since it is able to capture the
resulting $h\rightarrow bb$ decays.
At its highest masses, the main SR-High regions retain sensitivity to its
$ZZ$ decays, and SR-High-1J again visibly extends the projected exclusion.
At its lowest masses, SR-Int and SR-Low both contribute.
These light GMSB signal models have substantial contaminations in VR-Low, which
are seen in Figure~\ref{fig:2ljets_low_region} to exceed $50\%$ of the central
background.
That SR-Int also provides sensitivity here is some comfort that this signal
contamination does not entirely invalidate the result.
We do not consider off-shell GMSB models, so SR-OffShell regions do not exclude
any points alone here.

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_c1n2.pdf}
\caption{C1N2}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_gmsb.pdf}
\caption{GMSB}
\end{subfigure}
\caption[
Projected exclusion from sets of orthogonal signal regions
]{%
Projected exclusion from sets of orthogonal signal regions, demonstrating that
their combination has greater sensitivity reach than any individually.
The label `High' indicates the bins of SR-High, and `HighNo4' excludes
SR-High-1J to show the locations where mono-jet events have an impact.
Similarly, `$\llbb$', `Int', `Low', and `OffShell' are shown to target their
appropriate parameter spaces.
Although figures were produced before unblinding, with older samples and region
designs, their later updates do not change the general message.
Values of $\cls$ from expected (not observed --- the label is wrong) data in
the combined fit are overlaid on the grid.
}
\label{fig:2ljets_fit_multi_contours}
\end{figure}

@@
